Online Appendices for ``GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations''

### 2025-07-04 writeUps/appendix.tex

\usepackage{xr}
\externaldocument{paper}
\RequirePackage{amsmath,amsfonts,amssymb,amsthm}
%\RequirePackage[authoryear]{natbib}
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage[caption=false]{subfig}
\usepackage[doublespacing]{setspace}

@@

\input{notation.tex}

@@

\section{Appendix: Proofs and Calculations}
\subsection{Proof for Lemma \ref{lemma:expectation}}
As a preliminary, note that
% \begin{align*}
%   \EE[\st|\hpp]&=\EE\left\{\EE[\st|\pp,\hpp]|\hpp\right\}\\
%              &=\EE\left\{\EE[\st|\pp]|\hpp\right\}\\
%              &=\EE[\pp|\hpp]=\hpp
% \end{align*}

@@

%\clearpage

%\processdelayedfloats

%\setcounter{page}{1}

% \begin{center}
% \large
%     \textbf{Online Appendices for ``GEEPERs: Principal Stratification using Principal Scores and Stacked Estimating Equations''}
%   \end{center}
  \FloatBarrier
\section{Additional Simulation Results}
\FloatBarrier
\subsection{Plot of  AUC versus $\alpha$}
\FloatBarrier
\begin{center}

    \includegraphics[width=5.5in]{../simFigs/alphaAUC.pdf}

\end{center}
%\begin{table}
%\caption{Coverage of nominal 95\% confidence intervals}
%\clearpage

@@

\begin{table}
  \caption{Empirical coverage of nominal 95\% Confidence intervals for \geepers and \pmm when $n=500$ per condition.}
  \input{coverageTabAppendix500.tex}
 \end{table}

 \begin{table}
  \caption{Empirical coverage of nominal 95\% Confidence intervals for \geepers and \pmm when $n=1000$ per condition.}
  \input{coverageTabAppendix1000.tex}
 \end{table}

@@

The following table gives the root mean squared error (RMSE), $\left\{\sum_b (\hat{\tau}-\tau)^2/500\right\}^{1/2}$, for \textsc{geepers}, mixture model, and principal score weighting principal effect estimates under varying data generating models.\\

\begin{table}
  \caption{Empirical RMSE  for \geepers, \pmm, and \psw when $n=500$ per condition.}
  \input{rmseTabAppendix500}
 \end{table}

 \begin{table}
  \caption{Empirical RMSE  for \geepers, \pmm, and \psw when $n=1000$ per condition.}
  \input{rmseTabAppendix1000}
 \end{table}

@@

\FloatBarrier
\section{Additional Results from the OPT Study}
\FloatBarrier
\singlespacing
\FloatBarrier
\subsection{Summary Statistics}
\FloatBarrier
The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\

@@

\small
%\input{outcomeRegAppendix}
\input{psTab}

>>>>

\usepackage{xr}
\externaldocument{writeUps/paper}

\RequirePackage{amsmath,amsfonts,amssymb,amsthm}
%\RequirePackage[authoryear]{natbib}
\usepackage{longtable}
\usepackage{threeparttable}
\usepackage[caption=false]{subfig}
\usepackage[doublespacing]{setspace}

@@

\input{writeUps/notation.tex}

@@

\section{Appendix: Proofs and Calculations}
\subsection{Proof for Lemma \ref{lemma:expectation}}

As a preliminary, note that
% \begin{align*}
%   \EE[\st|\hpp]&=\EE\left\{\EE[\st|\pp,\hpp]|\hpp\right\}\\
%              &=\EE\left\{\EE[\st|\pp]|\hpp\right\}\\
%              &=\EE[\pp|\hpp]=\hpp
% \end{align*}

@@

  \FloatBarrier
\section{Additional Simulation Results}
\FloatBarrier
\subsection{Plot of  AUC versus $\alpha$}
\FloatBarrier

\begin{center}

    \includegraphics[width=5.5in]{simFigs/alphaAUC.pdf}

\end{center}

@@

\begin{table}
  \caption{Empirical coverage of nominal 95\% Confidence intervals for \geepers and \pmm when $n=500$ per condition.}
  \input{writeUps/coverageTabAppendix500.tex}
 \end{table}

 \begin{table}
  \caption{Empirical coverage of nominal 95\% Confidence intervals for \geepers and \pmm when $n=1000$ per condition.}
  \input{writeUps/coverageTabAppendix1000.tex}
 \end{table}

@@

=======
The following table gives the root mean squared error (RMSE), $\left\{\sum_b (\hat{\tau}-\tau)^2/500\right\}^{1/2}$, for \textsc{geepers}, mixture model, and principal score weighting principal effect estimates under varying data generating models.\\

\begin{table}
  \caption{Empirical RMSE  for \geepers, \pmm, and \psw when $n=500$ per condition.}
  \input{writeUps/rmseTabAppendix500}
 \end{table}

 \begin{table}
  \caption{Empirical RMSE  for \geepers, \pmm, and \psw when $n=1000$ per condition.}
  \input{writeUps/rmseTabAppendix1000}
 \end{table}

@@

\FloatBarrier
\section{Additional Results from the OPT Study}
\FloatBarrier
\singlespacing
\FloatBarrier
\subsection{Summary Statistics}
\FloatBarrier

The following table gives summary statistics for covariates and post-treatment outcomes in two of the conditions from the empirical study.\\

@@

\small
%\input{outcomeRegAppendix}

\input{psTab}
